\MakeUppercase{Layered Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-28 k-planar.tex
Small change

For each node $x\in V(K)$, define the \emph{separator}
\[
   S_x = \{v\in V(G): a(v)=x \} \enspace .
\]
Clearly $\mathcal{S}=\{S_x:x\in V(K)\}$ is a partition of $V(G)$.  We will use $\mathcal{S}$ as the partition that defines our quotient graph $H=G/\mathcal{S}$ with vertex set $V(H)=V(K)$ and the edge $xy\in E(H)$ if and only if there exists an edge $vw\in E(G)$ with $v\in S_x$ and $w\in S_y$.  First we argue that this partition has small width with respect to the layering $\{V_2,V_3,\ldots\}$ of $G^+$ defined by $T$ (recall that this is a layering of $G^+$, not a layering of $G$).

>>>>

For each node $x\in V(K)$, define the \emph{separator}
\[
   S_x = \{v\in V(G): a(v)=x \} \enspace .
\]
Clearly $\mathcal{S}=\{S_x:x\in V(K)\}$ is a partition of $V(G)$.  We will use $\mathcal{S}$ as the partition that defines our quotient graph $H=G/\mathcal{S}$ with vertex set $V(H)=V(K)$ and the edge $xy\in E(H)$ if and only if there exists an edge $vw\in E(G)$ with $v\in S_x$ and $w\in S_y$.  First we argue that this partition has small layered width with respect to the layering $\{V_2,V_3,\ldots\}$ of $G^+$ defined by $T$ (recall that this is a layering of $G^+$, not a layering of $G$).
